Supplementary Content for the article *The role of functional diversity in ecosystem regime shifts*

### 2022-03-30 experiments/2_supplement/supplement.Rmd
change title of supplement

---
title: Supplementary Content
subtitle: ??????Insert ms title???????
author: "Owen L Petchey, Rainer Krug, Marcel Suleiman, Romana Limberger, ???others???"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---

>>>>

---
title: Supplementary Content for the article *The role of functional diversity in ecosystem regime shifts*
author: "Owen L Petchey, plus all authors of the main article"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  bookdown::html_document2:
    toc: true
    toc_float:
      collapsed: true
      smooth_scroll: true
---
